### 2010-06-21 trunk/paper/IIWAS2010/content/introduction.tex
small updates to the introduction

When traveling though a jungle to a destination, it is easy to get
lost.  The first person to go somewhere may make a number of mistakes
in trying to find the best path to their destination.  However, those
who come later will find it easy to reach that destination if a
well-marked trail has been created. Olsen and Malizia describe this
idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
a user's search as a unique entity and working without an example
context, one can exploit the fact that a similar search may have been
performed already.  In one study, almost 40 percent of all queries
were found to be repetitions of previous queries\cite{1277770}. This
indicates the reuse of prior searches is a way to optimize the search
process.  Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer a user query. Using our analogy, Morpheus  follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.

The Morpheus system employs two types of users. One type is called a
\textit{guide user} who types queries in the Morpheus web interface and
searches for an answer to the query in an instrumented web browser that can
track answer pathways for a given query. This web tracking tool stores the query
and necessary information to revisit the pathways to the page where he or she
finds the answer. It also provides users a mechanism to highlight the answers.
The other type is a \textit{regular user}, who uses the Morpheus system much
like a regular search engine with a natural language interface. He can type a
question in a text box and receive a response from the system. The system
exploits previously answered queries to answer new questions.

>>>>

When traveling though a jungle to a destination, it is easy to get
lost.  The first person to go somewhere may make a number of mistakes
in trying to find the best path to their destination.  However, those
who come later will find it easy to reach that destination if a
well-marked trail has been created. Olsen and Malizia describe this
idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
a user's discovery experience as a unique entity and working without an example
context, one can exploit the fact that a similar search may have been
performed already.  In one study, almost 40 percent of all queries
were found to be repetitions of previous queries\cite{1277770}. This
indicates the reuse of prior searches is a way to optimize the search
process.  Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query. Using our analogy, Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.

The Morpheus system employs two types of users. The first user type, or \textit{guide user}, types queries into the Morpheus interface and subsequently searches for an answer to the query in an instrumented web browser.  This web browser is fitted with a browser plug-in that stores the query and collects information necessary to revisit the pathways to the answer. It also allows the user to highlight answers and other metadata.
The second user, searches the Morpheus system much
like a typical search engine with a natural language interface. She can type a
question in a text box and receive a response from the system. The system
exploits previously answered queries to answer new questions.
